Supporting Information for Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy

### 2024-09-25 paper.tex
starting edits

\autoref{fig:comparisonwmel} shows both HDFG and HSFG processes and compares them with related spectroscopies that investigate vibrational-electronic coupling.
The three-wave mixing ($\chi^{(2)}$) techniques are often less applicable as they require macroscopic non-centrosymmetry under the electric dipole approximation.\cite{RN480}
Hyper-Raman scattering itself is a six-wave mixing ($\chi^{(5)}$) technique; stimulated hyper-Raman will be weak and susceptible to four-wave mixing (FWM) cascades.\cite{RN515, RN243, Cho2000_Cascade}
A coherent six-wave mixing analogue of hyper-Raman scattering, coherent anti-Stokes hyper-Raman spectroscopy (CAHRS), has been proposed and explored theoretically by several authors; however, it is also weak and highly susceptible to FWM cascades.\cite{Berger1978, Bjarnason1980, Cho1997, Cho1998}
Of the many four-wave mixing techniques, HDFG and HSFG have strong similarity to Raman, stimulated Raman, and RISRS in that the electronic state must remove or add a $v$ quantum to the ground state (``ev'' coupling).
With the other four-wave and six-wave mixing techniques (\autoref{fig:comparisonwmel}, second row), the output signal depends on more states than just a single vibrational mode and electronic state (``evx'' coupling).\cite{RN445, RN335} 
As a result, the relationship between the output and vibrational-electronic coupling is more detailed, but also more complicated.
HDFG, HSFG and Raman are more direct probes of electronic-vibrational coupling.
Notably, HDFG and HSFG can be implemented as two-color experiments (with $\omega_2=\omega_3$);\cite{Cho2001} vibrational sum frequency generation (vSFG) or difference frequency generation (vDFG) setups can be trivially reconfigured to perform HSFG or HDFG measurements, respectively, to investigate ev coupling in bulk systems.

@@

In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
Coherent spectroscopies are often described using the density matrix formalism, where a density matrix $\rho$ is propagated using the Liouville-von Neumann equation $via$
\begin{equation}\label{LVNE}
	\dot{\rho} = \frac{1}{i \hbar} [H + V(t), \rho] + \dot{\rho}_R,
\end{equation}
where $H$ is the (static) system Hamiltonian, $V(t)$ is the field-matter interaction and $\rho_R$ is the relaxation density matrix. \cite{RN455}
In systems where interactions with surroundings are relevant, $\dot{\rho}_R$ becomes a complex function that can be modified to include phenomena such as system-bath interactions, solvent-solute coupling, among others. \cite{Sung2001}
In the limit where input field pulsewidths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write $\dot{\rho}_R \approx \Gamma \rho$, i.e. exponential relaxation, where $\Gamma$ is the system's dephasing rate. \cite{RN455, Sung2001}
While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Yan1988, Li1994, Myers1997} our goal is to introduce simple, quantitative models to understand HDFG response.
Thus, we write $\dot{\rho}_R = \Gamma \rho$.
The exponential relaxation limit has proven useful in investigating the properties of 2D-EV, 2D-VE, and doubly resonant SFG using pulses much longer than electronic dephasing times. \cite{Raschke2002, Gaynor2017}

>>>>

\autoref{fig:comparisonwmel} shows both HDFG and HSFG processes and compares them with related spectroscopies that investigate vibrational-electronic coupling.
The three-wave mixing ($\chi^{(2)}$) techniques are often less applicable as they require macroscopic non-centrosymmetry under the electric dipole approximation.\cite{RN480}
Hyper-Raman scattering itself is a six-wave mixing ($\chi^{(5)}$) technique; stimulated hyper-Raman will be weak and susceptible to four-wave mixing (FWM) cascades.\cite{RN515, RN243, Cho2000_Cascade}
A coherent six-wave mixing analogue of hyper-Raman scattering, coherent anti-Stokes hyper-Raman spectroscopy (CAHRS), has been proposed and explored theoretically by several authors; however, it is also weak and highly susceptible to FWM cascades.\cite{Taran1977, Berger1978, Bjarnason1980, Cho1997, Cho1998}
Of the many four-wave mixing techniques, HDFG and HSFG have strong similarity to Raman, stimulated Raman, and RISRS in that the electronic state must remove or add a $v$ quantum to the ground state (``ev'' coupling).
With the other four-wave and six-wave mixing techniques (\autoref{fig:comparisonwmel}, second row), the output signal depends on more states than just a single vibrational mode and electronic state (``evx'' coupling).\cite{RN445, RN335} 
As a result, the relationship between the output and vibrational-electronic coupling is more detailed, but also more complicated.
HDFG, HSFG and Raman are more direct probes of electronic-vibrational coupling.
Notably, HDFG and HSFG can be implemented as two-color experiments (with $\omega_2=\omega_3$);\cite{Cho2001} vibrational sum frequency generation (vSFG) or difference frequency generation (vDFG) setups can be trivially reconfigured to perform HSFG or HDFG measurements, respectively, to investigate ev coupling in bulk systems.

@@

In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
Coherent spectroscopies are often described using the density matrix formalism, where an n$^{th}$ order density matrix $\rho^{(n)}$ is propagated using the Liouville-von Neumann equation $via$
\begin{equation}\label{LVNE}
	\dot{\rho}^{(n)} = \frac{1}{i \hbar} [H + V(t), \rho^{(n-1)}] + \dot{\rho}^{(n)}_R,
\end{equation}
where $H$ is the (static) system Hamiltonian, $V(t)$ is the field-matter interaction and $\rho_R$ is the relaxation density matrix. \cite{RN455}
In systems where interactions with surroundings are relevant, $\dot{\rho}_R$ becomes a complex function that can be modified to include phenomena such as system-bath interactions, solvent-solute coupling, among others. \cite{Sung2001}
In the limit where input field pulsewidths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write $\dot{\rho}_R \approx \Gamma \rho$, i.e. exponential relaxation, where $\Gamma$ is the system's dephasing rate. \cite{RN455, Sue1986, Sung2001}
While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Sue1986, Yan1988, Li1994, Myers1997} our goal is to introduce simple, quantitative models to understand HDFG response.
Thus, we write $\dot{\rho}_R = \Gamma \rho$.
The exponential relaxation limit has proven useful in investigating the properties of 2D-EV, 2D-VE, and doubly resonant SFG using pulses much longer than electronic dephasing times. \cite{Raschke2002, Gaynor2017}

### 2024-09-25 si.tex
develop ht section
updated integral formulas
fixed a sign error with Delta; still suspicious of typos
fix <1|q|1> typo
starting edits

In this section, we discuss the evaluation of Herzberg-Teller integrals when the ground and first excited state are harmonic wells of identical curvature.\cite{HerzbergTeller1933}
% We note that Myers et al. have developed a general expression to evaluate Franck-Condon factors for two displaced harmonic wells of differing curvature,\cite{Myers1982} 
We investigate the one dimensional case using the Hamiltonian described in the main text, $H = H_g |g) \left(g| + H_e |e\right) (e|$, where
\begin{subequations}\label{Hamiltonian}
	\begin{equation}
		H_g = \frac{\hbar \omega }{2} \left(p^2 + q^2 \right)
	\end{equation}
	and
	\begin{equation}
		H_e = \frac{\hbar \omega }{2} \left(p^2 +  (q-\Delta)^2 \right) + \hbar \omega_{eg}.
	\end{equation} 
\end{subequations}
Here, $p,q$ are the dimensionless conjugate normal mode coordinates, $\hbar\omega_{eg}$ is the energy difference between $H_e$ and $H_g$, and $\Delta$ is the dimensionless offset of the excited state surface relative to the ground state.
The Hamiltonians are the well-known quantum harmonic oscillator, and their solutions are
\begin{equation}
	\psi_m(q) = \langle q | m \rangle = N_m H_m(q) \exp(-q^2/2),
\end{equation}
where $N_m = (m! \ 2^m \pi^{\frac{1}{2}})^{-\frac{1}{2}}$ is the normalization factor and $H_m$ is the $m^{th}$ Hermite Polynomial.\cite{RN230}

For an $n$-quantum excited state vibration $| \tilde{n} \rangle$, and a $m$-quantum ground state vibration $| \tilde{m} \rangle$, the $k^{th}$-order vibrational coupling term is
\begin{equation}
	\begin{split}
		\mel{\tilde{n}}{q^k}{m} &= \int_{-\infty}^\infty \mathrm{d}q \ \psi^*_n(q-\Delta) q^k \psi_m(q)\\
		&= \int_{-\infty}^\infty \mathrm{d}q \ N_n H_n(q-\Delta) \exp(-\frac{(q - \Delta)^2}{2}) q^k N_m H_m(q) \exp(-\frac{q^2}{2}). \\
		&= N_n N_m \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ H_n(q-\Delta) q^k H_m(q) \exp(-q^2 + q\Delta)
	\end{split}\label{key}
\end{equation}
The integral corresponds to Franck-Condon matrix elements for $k=0$ and Herzberg-Teller matrix elements for $k=1$.

\subsection{General Solution to $\langle \tilde{n} | q^k | m \rangle$}
The matrix elements of \autoref{key} can be computed numerically, but analytic forms of the integral also exist. 
Due to the polynomial nature of $H_v(q)$, the product $H_n(q-\Delta) q^k H_m(q)$ will also be a polynomial, so that the integral of equation \autoref{key} will be of the form
\begin{eqnarray}
	\int dq \ P_{nmk}(q) \exp(-q^2 + q\Delta), \\
	P_{nmk}(q) \equiv \sum_\lambda^{n+m+k} a_\lambda q^\lambda
\end{eqnarray}
for some set coefficients $a_\lambda$, to be specified later. We can recast the integral into the linear combination of integrals,
\begin{equation}\label{eq:analytic_form}
	\mel{\tilde{n}}{q^k}{m} = N_n N_m \exp(-\frac{\Delta^2}{2}) \sum_\lambda a_\lambda F_\lambda(\Delta),
\end{equation}
where
\begin{equation}\label{integral}
	F_w(\Delta) \equiv \int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta).
\end{equation}
\autoref{integral} can be readily evaluated, as we now show.  When $w=0$, the integral is evaluated by completing the square:\footnote{$\int_{-\infty}^{\infty} \mathrm{d}x \exp(-(x-a)^2) = \sqrt{\pi}$}
\begin{equation}
	\begin{split}
		F_0(\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \exp(-(q^2 - q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
		&= \exp(\frac{\Delta^2}{4}) \int_{-\infty}^\infty \mathrm{d}q \exp(-(q - \frac{\Delta}{2})^2) \\
		&= \sqrt{\pi} \exp(\frac{\Delta^2}{4})
	\end{split}
\end{equation}
For the general solution, \autoref{integral} is evaluated via repeated use of a well-known Gaussian identity
\begin{equation}\label{identity}
	\begin{split}
		F_w(\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta) = \partial_{\Delta} \int_{-\infty}^\infty \mathrm{d}q \ q^{w-1} \exp(-q^2 + q\Delta) \\
		&= \partial_\Delta F_{w-1}(\Delta)
	\end{split}
\end{equation}
so we can write
\begin{equation}\label{eq:F_solved}
	\begin{split}
		F_w(\Delta) &= \left(\partial_\Delta \right)^w F_0(\Delta) \\
		&= \sqrt{\pi} \frac{\mathrm{d}^w}{\mathrm{d}\Delta^w} \exp(\frac{\Delta^2}{4}) \\
		&= \sqrt{\pi} \left( -\frac{i}{2} \right)^w \exp(\frac{\Delta^2}{4}) H_w\left(i\frac{\Delta}{2}\right).
	\end{split}
\end{equation}
In the last line we have used the generator definition of Hermite polynomials:  $H_n(x) \equiv (-1)^n e^{x^2} \frac{\mathrm{d}^n}{\mathrm{d}x^n} e^{-x^2}$.

We now will evaluate the polynomial coefficients $P(q)$.
The Hermite polynomials of \autoref{key} can be explicitly written as 
\begin{equation}
\begin{split}
	H_m(q) &= \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} a_m^{(m-2x)} q^{m-2x} \\
	H_n(q-\Delta) &= \sum_{x=0}^{\left\lfloor{n/2}\right\rfloor}
	a_n^{(n-2x)} (q-\Delta)^{n-2x} \\
		&= \sum_{x=0}^{\left\lfloor{n/2}\right\rfloor} a_n^{(n-2x)} \sum_{l=0}^{n-2x} \Delta^{n-2x-l} \binom{n-2x}{l} q^l
\end{split}
\end{equation}
where $\left\lfloor n \right\rfloor$ denotes the \textit{floor} of $n$, $\binom{a}{b} = a! / (b!(a-b)!)$, and the Hermite coefficients are
\begin{equation}
	a_n^{(n-2x)} = n! \frac{(-1)^x 2^{n-2x}}{x!(n-2x)!}.
\end{equation}
Multiplying these terms together give us explicit polynomial coefficients:
\begin{equation}\label{eq:poly_solved}
\begin{split}
	P_{nmk}(q) %&= \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} a_m^{(m-2x)} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} a_n^{(n-2y)} \sum_{l=0}^{n-2y} \Delta^{n-2y-l} \binom{n-2y}{l} q^{l+m-2x+k} \\
	&= \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} c_{xyl} \ q^{l+m-2x+k}, \\
	c_xyl &= a_m^{(m-2x)} a_n^{(n-2y)} \Delta^{n-2y-l} \binom{n-2y}{l}.
\end{split}
\end{equation}
\autoref{eq:poly_solved} is not in standard polynomial form, because our summation is not singular and coefficients in our summation may have the same power. 
Further simplifications can be made to sum to reduce recounting indices, but we do not find these simplifications essential.
Regardless, substituting \autoref{eq:F_solved} and \autoref{eq:poly_solved} into \autoref{eq:analytic_form}, we can now evaluate the solution as:
\begin{equation}\label{eq:general_solution}
	\mel{\tilde{n}}{q^k}{m} = \sqrt{\pi} N_n N_m \exp(-\frac{\Delta^2}{4}) \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+m-2x+k} c_{xyl} H_{l+m-2x+k}\left(i\frac{\Delta}{2}\right).
\end{equation}

\subsection{Evaluating Herzberg Teller terms for HDFG}

\begin{equation}
\begin{split}
	\langle n |q| 0 \rangle &= \cdots \\
\end{split}
\end{equation}

\begin{equation}
	\begin{split}
		\langle n |q| 1 \rangle &= \cdots \\
	\end{split}
\end{equation}

% We now have the background needed to calculate $\langle \tilde{n} |q| m \rangle$.
% % $\mel{\tilde{1}}{q}{0}$ for an arbitrary offset $\Delta$.
% Using $H_0(q) = 1$ and $H_1(q) = 2q$,
% \begin{equation}\label{HT10}
% 	\begin{split}
% 		\mel{\tilde{1}}{q}{0} &= N_1 N_0 \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ 2(q - \Delta) q \exp(-q^2 + q\Delta)\\
% 		&= 2N_1 N_0 \exp(-\frac{\Delta^2}{2}) \left( \int_{-\infty}^\infty \mathrm{d}q \ q^2 \exp(-q^2 + q\Delta) + \Delta \int_{-\infty}^\infty \mathrm{d}q \ q \exp(-q^2 + q\Delta) \right)
% 	\end{split}
% \end{equation}
% Both integrals can be evaluated using \autoref{identity}:
% \begin{subequations}\label{evalGaussians}
% 	\begin{equation}
% 		\begin{split}
% 					\int_{-\infty}^\infty \mathrm{d}q \ q \exp(-q^2 + q\Delta) &= \partial_{\Delta} \left(\sqrt{\pi} \exp(\frac{\Delta^2}{4})\right)\\
% 					& = \sqrt{\pi} \frac{\Delta}{2} \exp(\frac{\Delta^2}{4})
% 		\end{split}
% 	\end{equation}
% 	\begin{equation}
% 	\begin{split}
% 		\int_{-\infty}^\infty \mathrm{d}q \ q^2 \exp(-q^2 + q\Delta) &= \partial_{\Delta} \left(\sqrt{\pi} \left(\frac{\Delta}{2} \exp(\frac{\Delta^2}{4})\right)\right)\\
% 		& =\sqrt{\pi} \left(\frac{1}{2}\exp(\frac{\Delta^2}{4}) + \frac{\Delta^2}{4} \exp(\frac{\Delta^2}{4})\right)
% 	\end{split}
% \end{equation}
% \end{subequations}
% Substituting the results of \autoref{evalGaussians} into \autoref{HT10}, 
% \begin{equation}
% 	\mel{\tilde{1}}{q}{0} = \sqrt{\frac{1}{2}} (1 - \frac{\Delta^2}{2}) \exp(\frac{-\Delta^2}{4})
% \end{equation}
% The evaluation of other Herzberg-Teller integrals is analogous.

\newpage
\section{Impact of displacement, resonance frequencies, and vibronic linewidth and on HDFG Spectra}
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/fcht.png}
	\caption{Plots of select (a) Franck-Condon factors and (b) Herzberg-Teller integrals relevant to this manuscript as a function of offset, $\Delta$.} 
	\label{fig:fcht}
\end{figure}

>>>>

In this section, we discuss the evaluation of Herzberg-Teller integrals when the ground and first excited state are harmonic wells of identical curvature.\cite{HerzbergTeller1933}
% We note that Myers et al. have developed a general expression to evaluate Franck-Condon factors for two displaced harmonic wells of differing curvature,\cite{Myers1982} 
We investigate the one dimensional case using the Hamiltonian described in the main text, $H = H_g |g) \left(g| + H_e |e\right) (e|$, where
\begin{subequations}\label{Hamiltonian}
	\begin{equation}
		H_g = \frac{\hbar \omega }{2} \left(p^2 + q^2 \right)
	\end{equation}
	and
	\begin{equation}
		H_e = \frac{\hbar \omega }{2} \left(p^2 +  (q-\Delta)^2 \right) + \hbar \omega_{eg}.
	\end{equation} 
\end{subequations}
Here, $p,q$ are the dimensionless conjugate normal mode coordinates, $\hbar\omega_{eg}$ is the energy difference between $H_e$ and $H_g$, and $\Delta$ is the dimensionless offset of the excited state surface relative to the ground state.
The Hamiltonians are the well-known quantum harmonic oscillator, and their position space wavefunctions are
\begin{equation}
	\psi_m(q) = \langle q | m \rangle = N_m H_m(q) \exp(-q^2/2),
\end{equation}
where $N_m = (m! \ 2^m \pi^{\frac{1}{2}})^{-\frac{1}{2}}$ is the normalization factor and $H_m$ is the $m^{th}$ Hermite Polynomial.\cite{RN230, MorseFeshbach}

For an $n$-quantum excited state vibration $| \tilde{n} \rangle$, and a $m$-quantum ground state vibration $\ket{m}$, the $k^{th}$-order vibrational coupling term is
\begin{equation}
	\begin{split}
		\mel{\tilde{n}}{q^k}{m} &= \int_{-\infty}^\infty \mathrm{d}q \ \psi^*_n(q-\Delta) q^k \psi_m(q)\\
		&= \int_{-\infty}^\infty \mathrm{d}q \ N_n H_n(q-\Delta) \exp(-\frac{(q - \Delta)^2}{2}) q^k N_m H_m(q) \exp(-\frac{q^2}{2}). \\
		&= N_n N_m \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ H_n(q-\Delta) q^k H_m(q) \exp(-q^2 + q\Delta)
	\end{split}\label{key}
\end{equation}
The integral corresponds to Franck-Condon factors for $k=0$ and Herzberg-Teller matrix elements for $k=1$.

\subsection{General Solution to $\langle \tilde{n} | q^k | m \rangle$}
The matrix elements of \autoref{key} can be computed numerically, but analytic forms of the integral also exist. 
Due to the polynomial nature of $H_v(q)$, the product $H_n(q-\Delta) q^k H_m(q)$ will also be a polynomial, so that the integral of equation \autoref{key} will be of the form
\begin{eqnarray}
	\int_{-\infty}^\infty \mathrm{d}q \ P_{nmk}(q) \exp(-q^2 + q\Delta), \\
	P_{nmk}(q) \equiv \sum_\lambda^{n+m+k} a_\lambda q^\lambda
\end{eqnarray}
for some set coefficients $a_\lambda$, to be specified later. We can recast the integral into the linear combination of integrals,
\begin{equation}\label{eq:analytic_form}
	\mel{\tilde{n}}{q^k}{m} = N_n N_m \exp(-\frac{\Delta^2}{2}) \sum_\lambda a_\lambda F_\lambda(\Delta),
\end{equation}
where
\begin{equation}\label{integral}
	F_w(\Delta) \equiv \int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta).
\end{equation}
\autoref{integral} can be readily evaluated, as we now show.  When $w=0$, the integral is evaluated by completing the square:\footnote{$\int_{-\infty}^{\infty} \mathrm{d}x \exp(-(x-a)^2) = \sqrt{\pi}$}
\begin{equation}
	\begin{split}
		F_0(\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \exp(-(q^2 - q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
		&= \exp(\frac{\Delta^2}{4}) \int_{-\infty}^\infty \mathrm{d}q \exp(-(q - \frac{\Delta}{2})^2) \\
		&= \sqrt{\pi} \exp(\frac{\Delta^2}{4})
	\end{split}
\end{equation}
For the general solution, \autoref{integral} is evaluated via repeated use of a well-known Gaussian identity
\begin{equation}\label{identity}
	\begin{split}
		F_w(\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta) = \partial_{\Delta} \int_{-\infty}^\infty \mathrm{d}q \ q^{w-1} \exp(-q^2 + q\Delta) \\
		&= \partial_\Delta F_{w-1}(\Delta)
	\end{split}
\end{equation}
so we can write\footnote{Setting $-x^2 \ = \ \Delta^2/4$ (so that $x \ = \ i \Delta /2$) and using the chain rule ($\mathrm{d}/\mathrm{d}x = \mathrm{d}/\mathrm{d}\Delta \ \mathrm{d}\Delta / \mathrm{d}x$) provides the final result in \autoref{eq:F_solved}}
\begin{equation}\label{eq:F_solved}
	\begin{split}
		F_w(\Delta) &= \left(\partial_\Delta \right)^w F_0(\Delta) \\
		&= \sqrt{\pi} \frac{\mathrm{d}^w}{\mathrm{d}\Delta^w} \exp(\frac{\Delta^2}{4}) \\
		&= \sqrt{\pi} \left( -\frac{i}{2} \right)^w \exp(\frac{\Delta^2}{4}) H_w\left(i\frac{\Delta}{2}\right).
	\end{split}
\end{equation}
In the last line we have used the generator definition of Hermite polynomials:  $H_n(x) \equiv (-1)^n e^{x^2} \frac{\mathrm{d}^n}{\mathrm{d}x^n} e^{-x^2}$.

We now will evaluate the polynomial coefficients $P(q)$.
The Hermite polynomials of \autoref{key} can be explicitly written as 
\begin{equation}
\begin{split}
	H_m(q) &= \sum_{s=0}^{\left\lfloor{m/2}\right\rfloor} a_m^{(m-2s)} q^{m-2s} \\
	H_n(q-\Delta) &= \sum_{s=0}^{\left\lfloor{n/2}\right\rfloor}
	a_n^{(n-2s)} (q-\Delta)^{n-2s} \\
		&= \sum_{s=0}^{\left\lfloor{n/2}\right\rfloor} a_n^{(n-2s)} \sum_{l=0}^{n-2s} \left(-\Delta\right)^{n-2s-l} \binom{n-2s}{l} q^l
\end{split}
\end{equation}
where $\left\lfloor n \right\rfloor$ denotes the \textit{floor} of $n$, $\binom{a}{b} = a! / (b!(a-b)!)$, and the Hermite coefficients are\cite{MorseFeshbach}
\begin{equation}
	a_n^{(n-2s)} = n! \frac{(-1)^x 2^{n-2s}}{s!(n-2s)!}.
\end{equation}
Multiplying these terms together give us explicit polynomial coefficients:
\begin{equation}\label{eq:poly_solved}
\begin{split}
	P_{nmk}(q) %&= \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} a_m^{(m-2x)} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} a_n^{(n-2y)} \sum_{l=0}^{n-2y} \Delta^{n-2y-l} \binom{n-2y}{l} q^{l+m-2x+k} \\
	&= \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} c_{xyl} \ q^{l+m-2x+k}, \\
	c_{xyl} &= a_m^{(m-2x)} a_n^{(n-2y)} \left(-\Delta\right)^{n-2y-l} \binom{n-2y}{l}.
\end{split}
\end{equation}
\autoref{eq:poly_solved} is not in standard polynomial form, because our summation is not singular and coefficients in our summation may have the same power. 
Further simplifications can be made to sum to reduce recounting indices, but we do not find these simplifications essential.
Regardless, substituting \autoref{eq:F_solved} and \autoref{eq:poly_solved} into \autoref{eq:analytic_form}, we can now evaluate the solution as:
\begin{equation}\label{eq:general_solution}
	\mel{\tilde{n}}{q^k}{m} = \sqrt{\pi} N_n N_m 
	\exp(-\frac{\Delta^2}{4}) \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+m-2x+k} c_{xyl} H_{l+m-2x+k}\left(i\frac{\Delta}{2}\right).
\end{equation}

\subsection{Evaluating Herzberg Teller terms for HDFG}
When starting from $\ket{0}$,
\begin{equation}
\begin{split}
	\langle \tilde{n} |q| 0 \rangle &= 
	\sqrt{\pi} N_n N_0 \exp(-\frac{\Delta^2}{4}) \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+1} c_{0yl} H_{l+1}\left(i\frac{\Delta}{2}\right) \\
	&= \sqrt{n! \ 2^n} \exp(-\frac{\Delta^2}{4})
	\sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} 
	\frac{(-1)^y}{2^{2y}y!}
	\sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+1} 
	\frac{\left(-\Delta\right)^{n-2y-l}}{l!(n-2y-l)!}
	H_{l+1}\left(i\frac{\Delta}{2}\right)
\end{split}
\end{equation}
giving the first few relevant integrals as
\begin{equation}
	\langle \tilde{0} |q| 0 \rangle = \frac{\Delta}{2} \exp(-\frac{\Delta^2}{4})
\end{equation}

\begin{equation}
	\langle \tilde{1} |q| 0 \rangle = 
	\frac{\sqrt{2}}{4} \left( 2 - \Delta^2 \right)
	\exp(-\frac{\Delta^2}{4})
\end{equation}

\begin{equation}
	\langle \tilde{2} |q| 0 \rangle = 
	\frac{\sqrt{2}}{8} \left( \Delta^3 - 4 \Delta \right)
	\exp(-\frac{\Delta^2}{4})
\end{equation}

Similarly, when starting from $\ket{1}$, 
\begin{equation}
	\begin{split}
		\langle \tilde{n} |q| 1 \rangle &= \sqrt{\pi} N_n N_1 \exp(-\frac{\Delta^2}{4}) \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+2} c_{1yl} H_{l+2}\left(i\frac{\Delta}{2}\right) \\
		&= 
		\sqrt{n! \ 2^{n+1}} \exp(-\frac{\Delta^2}{4}) 
		\sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} 
		\frac{(-1)^y}{2^{2y}y!}
		\sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+2} 
		\frac{\left(-\Delta\right)^{n-2y-l}}{l!(n-2y-l)!}
		H_{l+2}\left(i\frac{\Delta}{2}\right)
	\end{split}
\end{equation}
giving
\begin{equation}
	\langle \tilde{0} |q| 1 \rangle = \frac{\sqrt{2}}{4}\left( \Delta^2 + 2 \right)
	\exp(-\frac{\Delta^2}{4})
\end{equation}
\begin{equation}
	\langle \tilde{1} |q| 1 \rangle = \frac{\sqrt{2}}{4}\left( -\Delta^3 + 2\Delta \right)
	\exp(-\frac{\Delta^2}{4})
\end{equation}
\begin{equation}
	\langle \tilde{2} |q| 1 \rangle = \frac{1}{8} \left( \Delta^4 - 6\Delta^2 + 8 \right)
	\exp(-\frac{\Delta^2}{4})
\end{equation}

\newpage
\section{Impact of displacement, resonance frequencies, vibronic linewidth and molecular parameters on HDFG Spectra}
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/fcht.png}
	\caption{Plots of select (a) Franck-Condon factors and (b) Herzberg-Teller integrals relevant to this manuscript as a function of offset, $\Delta$.} 
	\label{fig:fcht}
\end{figure}
